SeedLing: Building and using a seed corpus \\ for the Human Language Project

### 2014-03-22 docs/computEL/relwork.tex
submitted version

The Leipzig Corpora Collection (LCC)\footnote{http://corpora.uni-leipzig.de} \cite{biemann2007leipzig} provides download of corpora in 117 languages, and dictionaries in a number of others, bringing the total number of represented languages up to 230. The corpora are large, readily available, in plain text, and labelled with ISO language codes.

>>>>

The Leipzig Corpora Collection (LCC)\footnote{\url{http://corpora.uni-leipzig.de}} \cite{biemann2007leipzig} provides download of corpora in 117 languages, and dictionaries in a number of others, bringing the total number of represented languages up to 230. The corpora are large, readily available, in plain text, and labelled with ISO language codes.
